Processing of visual and non-visual naturalistic spatial information in the "parahippocampal place area"

### 2021-02-23 paper/main.tex
add rest of Simons feedback as To-Dos

\noindent Generally
\begin{itemize}
    \item Todo's are mostly comments and can be deleted if issue is solved by
        current phrasing
    \item position of figures and tables is very odd now but probably does not
        matter
\end{itemize}

@@

% AV design matrix
The design matrices of the first-level time-series GLM analysis comprised the
regressors for the stimulus features listed in Tables~\ref{tab:events} and
\ref{tab:events} for the movie and audio-description stimulus, respectively.
% AD regressors in AV
Additionally, the design for the movie stimulus also contained the
regressors based on nouns used by the audio-description's narrator to indicate
a switch to another setting (categories \texttt{se\_new} and \texttt{se\_old}),
in order to be able to implement cross-modal control contrasts.
% AV regressors in AV
Likewise, the audio-description design matrix included movie cut related regressors
listed Table~\ref{tab:events} (excluding \texttt{no\_cut}).
% both stimuli: null regressors
For both stimuli, a null regressor was used for any event category in a segment
for which no event of a category was present (e.g. no event of
\texttt{vpe\_old} in segment 3; Tab.~\ref{tab:events}).
% temporal derivatives
Temporal derivatives of all regressors were added to the design matrix to compensate for
regional differences \citep{friston1998event}.
% motion parameters
Lastly, six participant and run specific motion estimated (translation and rotation)
were also included.
% high-pass filtering
The design matrices were temporally filtered with the same high-pass filter (cutoff period of
\unit[150]{s}) as the BOLD time series.

@@

Given the rich naturalistic stimuli and the availability of various stimulus
feature annotations, there are several candidates for implementing contrasts to
identify hemodynamic activity congruent with the hypothesized processing of
spatial information in the PPA. However, while the rationale for any contrast
composition must be sound, the selection of a single implementation remains
arbitrary to some degree. Consequently, we computed multiple contrasts that are
listed in Table~\ref{tab:contrasts} for movie
and audio-description, respectively. For each stimulus we, subjectively, picked
a primary contrast for result presentation (the first one in each Table) based
on how well the average event within categories represents spatial and
non-spatial information, and the number of events in the stimulus.
An evaluation of the robustness of these results with respect to similar but
different contrasts is provided in the supplementary materials.

% AV: primary contrast
In the primary contrast for the movie stimulus, we contrasted cuts to a setting
that was not depicted before (\texttt{vse\_new}) to cuts merely switching the
camera position within a setting that was already established earlier in the
movie (\texttt{vpe\_old}), because the former are designed to orient the viewer
in the movie environment using wider-camera angles, whereas the latter can
afford to depict details of a scene.
% AD: primary contrast
In the primary contrast of the audio-description stimulus, we contrasted
mentions of buildings and landmarks (\texttt{geo}), and rooms and
geometry-defining objects (\texttt{groom}) with nouns referring to a
person's head or face (\texttt{fahead}), and other non-geometry related
categories (\texttt{body}, \texttt{bodypart}, \texttt{fahead}, \texttt{object},
\texttt{sex\_f}, \texttt{sex\_m}).

@@

@@

% AV intro
First, we analyzed data from the movie offering a visual but ecologically more
valid stimulation than static pictures.
% AV primary contrast
The movie's primary $t$-contrast that compared cuts to a setting that was not
depicted before to cuts within a recurring setting (\texttt{vse\_new >
vpe\_old}) yielded three significant clusters (Tab.~\ref{tab:res-av-group1},
Fig.~\ref{fig:group-slices}).
% PPA (others the clusters extend into).
One cluster spans across the midline and comprises parts of the intracalcarine
and cuneal cortex, the lingual gyrus and retrosplenial cortex, the occipital and
temporal fusiform gyrus, and the parahippocampal cortex (reported from posterior
to anterior) in both hemispheres.
% LOC
Two additional bilateral clusters are located in the superior lateral occipital
cortex.

@@

>>>>

\noindent Generally
\begin{itemize}
    \item Todo's are mostly comments and can be deleted if issue is solved by
        current phrasing
    \item maybe "do something with" dice-index
    \item position of figures and tables is very odd now but probably does not
        matter
\end{itemize}

@@

\todo[inline]{add a summary to the end of section 2.7 explaining in 2 sentences,
what regressors you will be focussing on -> easier for those that got confused
on the way}
% AV design matrix
The design matrices of the first-level time-series GLM analysis comprised the
regressors for the stimulus features listed in Tables~\ref{tab:events} and
\ref{tab:events} for the movie and audio-description stimulus, respectively.
% AD regressors in AV
Additionally, the design for the movie stimulus also contained the
regressors based on nouns used by the audio-description's narrator to indicate
a switch to another setting (categories \texttt{se\_new} and \texttt{se\_old}),
in order to be able to implement cross-modal control contrasts.
% AV regressors in AV
Likewise, the audio-description design matrix included movie cut related regressors
listed Table~\ref{tab:events} (excluding \texttt{no\_cut}).
% both stimuli: null regressors
For both stimuli, a null regressor was used for any event category in a segment
for which no event of a category was present (e.g. no event of
\texttt{vpe\_old} in segment 3; Tab.~\ref{tab:events}).
% temporal derivatives
Temporal derivatives of all regressors were added to the design matrix to compensate for
regional differences \citep{friston1998event}.
% motion parameters
Lastly, six participant and run specific motion estimated (translation and rotation)
were also included.
% high-pass filtering
The design matrices were temporally filtered with the same high-pass filter (cutoff period of
\unit[150]{s}) as the BOLD time series.

@@

\todo[inline]{"we, subjectively, picked a primary contrast" :-(  -> you actually
write "based on"}
%
Given the rich naturalistic stimuli and the availability of various stimulus
feature annotations, there are several candidates for implementing contrasts to
identify hemodynamic activity congruent with the hypothesized processing of
spatial information in the PPA. However, while the rationale for any contrast
composition must be sound, the selection of a single implementation remains
arbitrary to some degree. Consequently, we computed multiple contrasts that are
listed in Table~\ref{tab:contrasts} for movie and audio-description,
respectively. For each stimulus we, subjectively, picked a primary contrast for
result presentation (the first one in each Table) based on how well the average
event within categories represents spatial and non-spatial information, and the
number of events in the stimulus.  An evaluation of the robustness of these
results with respect to similar but different contrasts is provided in the
supplementary materials.

\todo[inline]{"vse, vno, vpe,..." are not really the most intuitive regressor
names -> ausschreiben, wo möglich}
% AV: primary contrast
In the primary contrast for the movie stimulus, we contrasted cuts to a setting
that was not depicted before (\texttt{vse\_new}) to cuts merely switching the
camera position within a setting that was already established earlier in the
movie (\texttt{vpe\_old}), because the former are designed to orient the viewer
in the movie environment using wider-camera angles, whereas the latter can
afford to depict details of a scene.
% AD: primary contrast
In the primary contrast of the audio-description stimulus, we contrasted
mentions of buildings and landmarks (\texttt{geo}), and rooms and
geometry-defining objects (\texttt{groom}) with nouns referring to a person's
head or face (\texttt{fahead}), and other non-geometry related categories
(\texttt{body}, \texttt{bodypart}, \texttt{fahead}, \texttt{object},
\texttt{sex\_f}, \texttt{sex\_m}).

@@

\todo[inline]{The presentation could be structured a bit more (subheadings,
paragraphs etc), as it is, it is quite a long flow of text and numbers -> check
instructions at scientific data}

\todo[inline]{SE: imo, key question is only partially answered: how close is
movie / audio to localizer". Can you corroborate figure 3 with some more
numbers? COH: schwierig vergleichbar (insb. unterschiedliche thresholds), daher
Bland-Altman-Plots -> mention that point at BA-Plots}

@@

\todo[inline]{"a visual but ecologically more valid stimulation" -> The "but"
doesn't make sense to me here -> add phrasing similar to the one used in the
(rephrased) intro}
% AV intro
First, we analyzed data from the movie offering a visual but ecologically more
valid stimulation than static pictures.
% AV primary contrast
The movie's primary $t$-contrast that compared cuts to a setting that was not
depicted before to cuts within a recurring setting (\texttt{vse\_new >
vpe\_old}) yielded three significant clusters (Tab.~\ref{tab:res-av-group1},
Fig.~\ref{fig:group-slices}).
% PPA (others the clusters extend into).
One cluster spans across the midline and comprises parts of the intracalcarine
and cuneal cortex, the lingual gyrus and retrosplenial cortex, the occipital and
temporal fusiform gyrus, and the parahippocampal cortex (reported from posterior
to anterior) in both hemispheres.
% LOC
Two additional bilateral clusters are located in the superior lateral occipital
cortex.
\todo[inline]{SE: What to make out of the fact that the movie stimulation seems
to evoke activation that goes substantially further caudal than the classical
PPA? COH: part of the discussion; maybe a concluding statement here}

@@

\todo[inline]{jeweils mit dem Befund, den Du diskutieren willst beginnen und mit
einer take-home message enden.}

\todo[inline]{Was mich etwas wundert, es gibt
doch schon andere "event-related" analysen von movies, oder? Die werden kaum
diskutiert. -> Studie, die etwas mit Event-related design zitieren;
NeuroScout-Framework oder. Pliers Studien zitieren}

\todo[inline]{Ebenso kommt mir das Potential (warum ist das relevant -> rich
stimulus ie many possible analyses, better compliance, easier to perform for
difficult populations, etc) eigentlich zu kurz}
